%%
%% Daniel Moraes | Resume
%%

\documentstyle[hyperref, margin, line]{resume}

\usepackage{enumitem}
\setlength{\leftmargini}{15pt}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.60in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.95in}

\renewcommand{\namefont}{\LARGE\emph}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

%%
%% the following code defines some macros for terms which have raised font
%% (ie 4\fourth would result 4th with the 'th' raised (superscripted)
%%

\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\CSharp{{\rm C\raise.5ex\hbox{\small \#}}}
% 'st' 'nd' 'rd' 'th' superscripts for numbers
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}

%%
%% starting the actual document
%%

\begin{document}

\name{Daniel Bastos Moraes}
\address{+55 19 98111{-}8214 $\cdot$ daniel.b.moraes@gmail.com $\cdot$ https://dmoraes.org}

\begin{resume}

\vspace{-0.2in}

%%
%% data scientist highlights
%%

\section{\textsc{Highlights}}

Over 10 years of work experience and strong computer science background.\vspace{0.4em}\\
Experienced with algorithms, machine learning, and computer vision techniques.\vspace{0.4em}\\
Solid skills in \Cplusplus, Python, SQL, and full stack web dev.\vspace{0.4em}\\
Self-directed learner and clear communication/documentation skills.

%%
%% software engineer hightlights
%%

% \section{\textsc{Highlights}}

% Over 10 years of work experience and strong computer science background.\vspace{0.4em}\\
% Solid skills in JavaScript, Python, \Cplusplus, and SQL\@.
% Solid skills in full stack web dev, including modern tools like React.js, Node.js, and REST APIs.\vspace{0.4em}\\
% Self-directed learner and clear communication/documentation skills.\vspace{0.4em}\\
% Can effectively communicate in English.

%%
%% education
%%

\begin{formatb}
  \employer{l}\dates{r}\\
  \title{r}\\
\end{formatb}

\section{\textsc{Education}}

\employer{\textbf{University of Campinas (Unicamp)} {--} {\small Campinas, Brazil}}
\dates{{\small 08/2011 {--} 02/2014}}
\title{\emph{Master of Computer Science}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Title: Low False Positive Learning with Support Vector Machines.
\item Advisor: Dr.\ Anderson Rocha.
\item Member of RECOD (Reasoning for Complex Data) lab.
\end{itemize}
\end{position}

\employer{\textbf{Tiradentes University (Unit)} {--} {\small Aracaju, Brazil}}
\dates{{\small 08/2007 {--} 12/2011}}
\title{\emph{Bachelor of Computer Science}}
\begin{position}
\begin{itemize}\small
\vspace{1mm}
\item Title: Automatic Relevance Ranking of Offers Based on their Features.
\item Advisor: M.Sc Fernando Henrique Bezerra Cardoso.
\item Highest MGP (GPA equivalent) in class.
\item Algorithms and Data Structures I TA\@.
\end{itemize}
\end{position}

%%
%% work experience
%%

\begin{formatb}
  \employer{l}\dates{r}\\
  \title{r}\\
\end{formatb}

\section{\textsc{Selected Work\\Experience}}

\employer{\textbf{HOOBOX Robotics} {--} {\small Campinas, Brazil}}
\dates{{\small Since 03/2018}}
\title{\emph{Software Engineer and Data Scientist}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Coordinate a team of two developers and two researchers.
\item Developed high precision algorithms for detecting facial expressions, on a team of three researchers.
\item Designed and implemented a new application for Wheelie with modern technologies.

\vspace{1mm}
{\small \emph{Tech}: TensorFlow, AWS, Scikit Learn, Docker, Python, Mongo, React, Node, CI, Shell, REST APIs.}
\end{itemize}
\end{position}

\employer{\textbf{UpWork} {--} {\small Remote Job}}
\dates{{\small Since 05/2017}}
\title{\emph{Data Scientist and Software Engineer}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Designed and implemented efficient algorithms for computing adaptive and random pairs.
\item Developed and launched a content management system for artworks. Available at https://myarthaus.com.
\item Implemented the major part of the frontend of a music streaming service. Available at https://stereo.co.

\vspace{1mm}
{\small \emph{Tech}: \Cplusplus, PostgreSQL, React, Node, Docker, CI, Shell, REST APIs, Testing.}
\end{itemize}
\end{position}

\employer{\textbf{Samsung Research Institute Brazil (via Unicamp)} {--} {\small Campinas, Brazil}}
\dates{{\small 03/2014 {--} 03/2016}}
\title{\emph{Data Scientist, Lead Software Engineer, Consultant}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Developed a method that detects porn audio with an accuracy of over 89.5\%.
\item Optimized and ported our learning pipeline to a mobile device, with
an speed gain of 63.5\%.
\item Developed and delivered real time porn and violence detection tools for Android and Linux.
\item One patent and second place at the VSD generalization task of MediaEval 2014 competition.
\item Analyzed and reported implementation issues on the SMA and VLFeat libraries.

\vspace{1mm}
{\small \emph{Tech}: \Cplusplus, Python, Android, Shell Script, OpenCV, LibSVM,
FFmpeg, openSMILE, VLFeat\@.}
\end{itemize}
\end{position}

\employer{\textbf{Regional Court of Sergipe (via CTIS)} {--} {\small Aracaju, Brazil}}
\dates{\small{12/2010 {--} 07/2011}}
\title{\emph{Software Engineer}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Developed a distributed Plone module that synchronizes every day hundreds
  of files in real-time.
\item Developed a module to automatically import thousands of documents to a Plone-based website.

\vspace{1mm}
{\small \emph{Tech}: Python, Plone\@.}
\end{itemize}
\end{position}

\employer{\textbf{Lumentech} {--} {\small Aracaju, Brazil}}
\dates{{\small 03/2009 {--} 04/2010}}
\title{\emph{Software Engineer, Intern}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Developed important features to a MMORPG web game, including groups,
  email, and pathfinding.
\item Developed the Roboto game, on a team of 1 engineer and 2 designers in
  3 months.
\item Developed the Axe Penny Paintball game, on a team of 3 engineers and
  1 designer in 1 month.

\vspace{1mm}
{\small \emph{Tech}: JavaScript, ActionScript, HTML/CSS\@.}
\end{itemize}
\end{position}

\employer{\textbf{Alfama Web} {--} {\small Aracaju, Brazil}}
\dates{{\small 02/2008 {--} 02/2009}}
\title{\emph{Software Engineer, Intern}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Implemented several features to an student information system.
\item Developed and delivered a system to register employee performance and
  several websites.

\vspace{1mm}
{\small \emph{Tech}: PHP, JavaScript, SQL (MySQL), HTML/CSS\@.}
\end{itemize}
\end{position}

%%
%% projects
%%

\begin{formatb}
  \employer{l}\dates{r}\\
\end{formatb}

\section{\textsc{Selected\\Projects}}

\employer{\textbf{Algorithms Training}}
\dates{{\small 06/2016 {--} 04/2017}}

\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Solved over 300 problems from Introduction to Algorithms, Third Edition (CLRS).
\item Solved and coded in \Cplusplus\ over 80 coding problems from different sources.
\item Theoretical solutions available online at http://clrs.dmoraes.org.
\item Coded solutions available online at https://github.com/danielmoraes/epi.

\vspace{1mm}
{\small \emph{Tech}: \Cplusplus, \LaTeX.}
\end{itemize}
\end{position}

\employer{\textbf{Crowd Detection with BinBoost Descriptors}}
\dates{{\small 03/2014 {--} 06/2014}}

\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Method to detect crowds on images {--} achieved an accuracy of over 94\%.
\item Developed on a team of two researchers.
\item Paper available online at https://dmoraes.org/projects.
\item Research conducted under supervision of Dr.\ Siome Goldenstein and
Dra.\ Sandra Avila.

\vspace{1mm}
{\small \emph{Tech}: Python, Shell Script, OpenCV, LibSVM, BinBoost.}
\end{itemize}
\end{position}

\employer{\textbf{Low False Positive Learning with Support Vector Machines}}
\dates{{\small 12/2012 {--} 02/2014}}

\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Novel 2-level learning method for low false positive classification.
\item Method’s effectiveness showed trough comparisons to other solutions in 33
  datasets.
\item Published on the 38th vol of the Journal of Visual Communication and Image Representation (JVCI).
\item Research conducted under supervision of Dr.\ Anderson Rocha and Dr.\
  Jacques Wainer.

\vspace{1mm}
{\small \emph{Tech}: Python, LibSVM.}
\end{itemize}
\end{position}

\employer{\textbf{Feature-Based Product Ranking}}
\dates{{\small 08/2012 {--} 12/2012}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item A product ranking algorithm based on SVMs that takes into account the
  cost-benefit ratio.
\item Agreement of 64\% according to a test conducted with 79 users.
\item Research conducted under supervision of Dr.\ Anderson Rocha.

\vspace{1mm}
{\small \emph{Tech}: Python, LibSVM, R, JavaScript, HTML/CSS\@.}
\end{itemize}
\end{position}

\employer{\textbf{Spider for Google Shopping and Buscape}}
\dates{{\small 05/2012 {--} 08/2012}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
  \item An HTML spider that collects products data from Google Shopping and
  Buscape.
\item Collected and refined data from 495,000 offers of laptops from Google
  Shopping during 7 months.

\vspace{1mm}
{\small \emph{Tech}: Python, LibSVM, JavaScript, SQL (MySQL), HTML/CSS\@.}
\end{itemize}
\end{position}

%%
%% organizations
%%

\begin{formatb}
  \employer{l}\dates{r}\\
  \title{r}\\
\end{formatb}

\section{\textsc{Organizations}}

\employer{\textbf{IEEE Image Forgery Detection Challenge}}
\dates{{\small Since 05/2013}}
\title{\emph{Technical Lead}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item Built and maintained the submission system and the website, on a team of
  2 engineers.
\item Available online at http://ifc.recod.ic.unicamp.br.

\vspace{1mm}
{\small \emph{Tech}: Python, Shell Script, SQL (PostgreSQL), JavaScript,
HTML/CSS\@.}
\end{itemize}
\end{position}

%%
%% teaching experience
%%

\begin{formatb}
  \employer{l}\dates{r}\\
  \title{r}\\
\end{formatb}

\section{\textsc{Teaching Experience}}

\employer{\textbf{Unraveling JavaScript}}
\dates{{\small 11/2010}}
\title{\emph{Short Course}}
\begin{position}
\vspace{1mm}
\begin{itemize}\small
\item JavaScript course presented to computer science students at Tiradentes
  University.
\end{itemize}
\end{position}

%%
%% skills
%%

\section{\textsc{Technical Skills}}

\emph{Programming}: \Cplusplus, Python, Shell Script, SQL, JavaScript (ES6),
Java/Android.\vspace{0.4em}\\
\emph{Frameworks/Tools}: GNU/Linux, AWS, R, OpenCV, Node.js, React.js/Redux,
Git, \LaTeX.\vspace{0.4em}\\
\emph{DevOps}: Docker, RabbitMQ, CI, Issue Tracker.

\end{resume}
\end{document}
